---
title: "Evaluation of a motor competence “proficiency barrier” to health-related fitness in youth"
author: "Cade Abrams and Bryan Terlizzi"
output:
  html_document
---

```{r include=FALSE}
library(here)
library(tidyverse)
library(semPower)
library(sjPlot)
library(qwraps2)
library(flextable)
library(officer)
library(apaTables)
library(irr)

library(bibtex) # For finding and creating citations
```

# Citations
```{r include=FALSE}
# using bibtex package

write.bib(c('apaTables', "officer", "sjPlot", "flextable", "qwraps2",
            "kableExtra", "tidyverse", "irr"), 
          file = "PB.bib", 
          append = TRUE, 
          verbose = TRUE)

```

### Checking for problems
```{r echo=FALSE}
PB <- read_csv(here("Data Files", "Clean Data", "PB.csv"))

# Making factors
PB <- PB %>% 
  mutate(Grip_level = factor(allo_grip_class,
                             levels = c(1, 2, 3),
                             labels = c("Low", "Moderate", "High")),
         Pacer_level = factor(PACER_HFZ,
                              levels = c(1, 2, 3),
                              labels = c("Health Risk", "Needs Improvement", "Healthy")),
         MC_level = factor(MCA_Class,
                           levels = c(1, 2, 3),
                           labels = c("Low", "Moderate", "High")))

# Making Sex and Ethnicity factors

PB <- PB %>% 
  mutate_at(c("Sex", "Ethnicity"), as.factor)

head(PB)

table(PB$Ethnicity)
```


## Descriptive Statistics
```{r echo=FALSE}
# Using qwraps2
descriptives <- subset(PB, select = c(MC_level, Sex, Ethnicity, Age_Test_yrs, StaHt, Weightkg, 
                                      BMI, PACER_VO2max, Grip_Max_Mean_kg))

descriptives

participants <- list("Age" = 
         list("min"       = ~ min(Age_Test_yrs),
              "mean (sd)" = ~ qwraps2 :: mean_sd(Age_Test_yrs),
              "max"       = ~ max (Age_Test_yrs)))

age <- summary_table(descriptives, participants)

age

PB %>%
  group_by(Sex, MC_level, Grip_level) %>%
  summarise(Sex_Count=n(), 
            BMI = mean(BMI),
          .groups = "drop")


gender_tib <- descriptives %>%
  group_by(Sex) %>%
  summarise(N = n()) %>%
  mutate(props = round(N/sum(N), 
                       digits = 3)) %>%
 ungroup

ethnic_tib <- descriptives %>%
  group_by(Ethnicity) %>%
  summarise(N = n()) %>%
  mutate(props = round(N/sum(N), 
                       digits = 3)) %>%
 ungroup
```

### APA Table for Descriptive Stats (Packages: qwraps2; flextable; officer)
```{r echo=FALSE}
options(qwraps2_markup = "markdown")
our_summary1 <-
  list("Height (cm)" =
       list("min"       = ~ min(StaHt),
            "median"    = ~ median(StaHt),
            "max"       = ~ max(StaHt),
            "mean (sd)" = ~ qwraps2::mean_sd(StaHt)),
       "Weight (kg)" =
       list("min"       = ~ min(Weightkg),
            "median"    = ~ median(Weightkg),
            "max"       = ~ max(Weightkg),
            "mean (sd)" = ~ qwraps2::mean_sd(Weightkg)),
       "Grip Max Average (kg)" =
       list("min"       = ~ min(Grip_Max_Mean_kg),
            "median"    = ~ median(Grip_Max_Mean_kg),
            "max"       = ~ max(Grip_Max_Mean_kg),
            "mean (sd)" = ~ qwraps2::mean_sd(Grip_Max_Mean_kg)),
       "Vo2 Max" =
       list("min"       = ~ min(PACER_VO2max),
            "median"    = ~ median(PACER_VO2max),
            "max"       = ~ max(PACER_VO2max),
            "mean (sd)" = ~ qwraps2::mean_sd(PACER_VO2max))
       )

whole <- summary_table(descriptives, our_summary1)
whole

level.sum <- summary_table(dplyr::group_by(descriptives, MC_level), our_summary1)
level.sum

level.sum <- as.data.frame(level.sum)

level.sum <- flextable(level.sum %>% rownames_to_column("Delete This Column Header"))

level.sum <- theme_booktabs(level.sum)

level.sum <- align(level.sum, align = "center", part = "body")

level.sum <- set_caption(level.sum, 
                          caption = "Descriptive Statistics of Scores on Level of Motor 
                                     Competence")

level.sum <- footnote(level.sum, 
                      i = 9, 
                      j = 1, 
                      value = as_paragraph("Grip Max Average was calculated by averaging 
                      maximum grip values for the right and left hands."))

level.sum <- autofit(level.sum)

level.sum

#word_export <- read_docx()
#word_export <- body_add_flextable(word_export, level.sum)
#print(word_export, 'new table.docx')
```

### Calculating ICC for All Tests (Motor & Grip)

#### KTK Platforms ICC
```{r echo=FALSE}
platforms <- PB[, c("KTKpf1", "KTKpf2")]

icc(platforms,
    model = "twoway",
    type = "agreement",
    unit = "single")

# Platforms ICC = .677 95%CI (.27, .834) Moderate ICC
```

#### Lateral Jumping
```{r echo=FALSE}
LJ <- PB[, c("KTKjump1", "KTKjump2")]

icc(LJ,
    model = "twoway",
    type = "agreement",
    unit = "single")

# Lateral Jumping ICC = .848 95%CI (.808, .88) Good ICC
```

#### Shuttle Run
```{r echo=FALSE}
SHR <- PB[, c("SHR1", "SHR2")]

icc(SHR,
    model = "twoway",
    type = "agreement",
    unit = "single")

# Shuttle Run ICC = .891 95%CI (.861, .915) Good ICC
```

#### SLJ ICC
```{r echo=FALSE}
jump <- PB[, c("SLJdistance1", "SLJdistance2", "SLJdistance3")]

icc(jump,
    model = "twoway",
    type = "agreement",
    unit = "single")

# Jump ICC = .933 95%CI (.918, .946) Excellent ICC
```

#### Throwing ICC
```{r echo=FALSE}
throw <- PB[, c("ThrowSpeed1_mph", "ThrowSpeed2_mph", "ThrowSpeed3_mph")]

icc(throw,
    model = "twoway",
    type = "agreement",
    unit = "single")

# Throw ICC = .949 95%CI (.937, .959) Excellent ICC
```

#### Kicking ICC
```{r}
kick <- PB[, c("KickSpeed1_mph", "KickSpeed2_mph", "KickSpeed3_mph")]

icc(kick,
    model = "twoway",
    type = "agreement",
    unit = "single")

# Kick ICC = .769 95%CI (.723, .809) Good ICC
```

#### Grip ICC
```{r echo=FALSE}
grip <- PB[, c("GripR1", "GripR2", "GripR3", "GripL1", "GripL2", "GripL3")]

icc(grip,
    model = "twoway",
    type = "agreement",
    unit = "single")

# Grip ICC = .921 95%CI (.899, .938) Excellent ICC
```

#### APA Correlation Table for Grip, V02, and MCA Overall (Packages: apaTables)
```{r}
correlations <- subset(PB, select = c(Sex, MCA_Overall, allo_grip_percentile, PACER_VO2max))

apa.cor.table(correlations, table.number = 2)#, filename = "New Correlation Table.doc")
```


## Looking at Cross Table for MSF (Packages: sjPlot)
```{r}
PB.new <- subset(PB, select=c(Sex, MC_level, Grip_level, Pacer_level))

sjt.xtab(PB.new$MC_level, 
         PB.new$Grip_level, 
         show.row.prc = TRUE, 
         show.legend = TRUE, 
         file = "apa_GRIP.doc")

ggplot(PB,aes(x = MC_level, y = allo_grip_class))+
  geom_violin()+
  geom_jitter(height = 0, width = 0.03)+
  stat_summary(fun = "mean", color = "red", geom = "point", size = 3)
```


## Looking at Cross Table for CRF (Packages: sjPlot)
```{r}
sjt.xtab(PB.new$MC_level, 
         PB.new$Pacer_level, 
         show.row.prc = TRUE, 
         show.legend = TRUE,  
         file = "apa_PACER.doc")

ggplot(PB,aes(x = PB$MCA_Overall, y = PB$PACER_VO2max)) +
  geom_point()
```


### Measuring Post Hoc Power (Packages: semPower)

```{r eval=FALSE, include=FALSE}
N <- nrow(PB)

a <- (length(unique(PB$MC_level))-1)*(length(unique(PB$PACER_HFZ))-1)
  
pwr.chisq.test(w = .217, N = N, df = a)

```

# Did not use any of the 95% CI below for differences between groups

##### Looking at 95% Confidence Interval for Difference Between Low and High MC for "Health-Risk" CRF
```{r eval=FALSE, include=FALSE}
CRF.diff <- ftable(PB.new$MC_Level, PB.new$PACER_Level)

CRF.prop <- prop.table(CRF.diff, margin = 2)

#Let's look at all the totals for this table.

sum(140+41+63)

# If there is no difference in conditions, here is our best
# estimate of the proportion of people who are considered a health risk in the population for CRF.

140/244

low_MC_CRF.ha = (140/244)*24
low_MC_CRF.ha

high_MC_CRF.ha = (140/244)*30
high_MC_CRF.ha

contrast.1 <- CRF.prop[1,1]-CRF.prop[3,1]
contrast.1

# We need the standard error.

se.1 <- sqrt(CRF.prop[1,1]*(1-CRF.prop[1,1])/244 +
               CRF.prop[3,1]*(1-CRF.prop[3,1])/244)
se.1

# Let's get Scheffe's critical value. Note that we can use this
# same value for any contrasts we decide to look at.

cv = sqrt(qchisq(.95, 4))
cv

# So here's our MOE for this contrast.

moe.1 <- se.1*cv
moe.1

# Here's our confidence interval boundaries.

contrast.1 - moe.1
contrast.1 + moe.1
```

#### Looking at 95% Confidence Interval for Dfference Between Low and High MC for "Healthy" CRF
```{r eval=FALSE, include=FALSE}

#Let's look at all the totals for this table.

sum(140+41+63)

# If there is no difference in conditions, here is our best
# estimate of the proportion of people who are considered a health risk in the population for CRF.

63/244

low_MC_CRF.ha = (63/244)*24
low_MC_CRF.ha

high_MC_CRF.ha = (63/244)*30
high_MC_CRF.ha

contrast.2 <- CRF.prop[3,3]-CRF.prop[1,3]
contrast.2

# We need the standard error.

se.2 <- sqrt(CRF.prop[1,3]*(1-CRF.prop[1,3])/244 +
               CRF.prop[3,3]*(1-CRF.prop[3,3])/244)
se.2

# Let's get Scheffe's critical value. Note that we can use this
# same value for any contrasts we decide to look at.

cv = sqrt(qchisq(.95, 4))
cv

# So here's our MOE for this contrast.

moe.2 <- se.2*cv
moe.2

# Here's our confidence interval boundaries.

contrast.2 - moe.2
contrast.2 + moe.2
```

#### Looking at 95% Confidence Interval for Dfference Between Low and High MC for "Low" MSF
```{r eval=FALSE, include=FALSE}
MSF.diff <- ftable(PB.new$MC_Level, PB.new$Grip_Level)

MSF.prop <-prop.table(MSF.diff, margin = 1)

#Let's look at all the totals for this table.

sum(38+124+82)

# If there is no difference in conditions, here is our best
# estimate of the proportion of people who are considered a health risk in the population for 
# CRF.

38/244

low_MC_MSF.ha = (38/244)*24
low_MC_MSF.ha

high_MC_MSF.ha = (38/244)*30
high_MC_MSF.ha

contrast.3 <- MSF.prop[1,1]-MSF.prop[3,1]
contrast.3

# We need the standard error.

se.3 <- sqrt(MSF.prop[1,1]*(1-MSF.prop[1,1])/244 +
               MSF.prop[3,1]*(1-MSF.prop[3,1])/244)
se.3

# Let's get Scheffe's critical value. Note that we can use this
# same value for any contrasts we decide to look at.

cv = sqrt(qchisq(.95, 4))
cv

# So here's our MOE for this contrast.

moe.3 <- se.3*cv
moe.3

# Here's our confidence interval boundaries.

contrast.3 - moe.3
contrast.3 + moe.3

```

#### Looking at 95% Confidence Interval for Dfference Between Low and High MC for "High" MSF
```{r eval=FALSE, include=FALSE}

#Let's look at all the totals for this table.

sum(38+124+82)

# If there is no difference in conditions, here is our best
# estimate of the proportion of people who are considered a health risk in the population for CRF.

82/244

low_MC_MSF.ha = (82/244)*24
low_MC_MSF.ha

high_MC_MSF.ha = (82/244)*30
high_MC_MSF.ha

contrast.4 <- MSF.prop[3,3]-MSF.prop[1,3]
contrast.4

# We need the standard error.

se.4 <- sqrt(MSF.prop[1,3]*(1-MSF.prop[1,3])/244 +
               MSF.prop[3,3]*(1-MSF.prop[3,3])/244)
se.4

# Let's get Scheffe's critical value. Note that we can use this
# same value for any contrasts we decide to look at.

cv = sqrt(qchisq(.95, 4))
cv

# So here's our MOE for this contrast.

moe.4 <- se.4*cv
moe.4

# Here's our confidence interval boundaries.

contrast.4 - moe.4
contrast.4 + moe.4
```

```{r}
cor.test(PB$MCA_Overall, PB$PACER_VO2max)
```

```{r}
cor.test(PB$MCA_Overall, PB$allo_grip_percentile)
```

```{r}
cor.test(PB$PerFat, PB$PACER_VO2max)
cor.test(PB$PerFat, PB$allo_grip_percentile)
cor.test(PB$PerFat, PB$MCA_Overall)

cor.test(PB$PerFat, PB$KTKpf2)
cor.test(PB$PerFat, PB$KTKjump2)
cor.test(PB$PerFat, PB$SLJdistance2)
cor.test(PB$PerFat, PB$ThrowSpeed2_mph)
cor.test(PB$PerFat, PB$KickSpeed2_mph)
cor.test(PB$PerFat, PB$SHR2)

chisq.test(PB$PerFat_HFZ, PB$MCA_Class)

sjt.xtab(PB$MC_level, 
         PB$PerFat_HFZ, 
         show.row.prc = TRUE, 
         show.legend = TRUE)

sjt.xtab(PB$PACER_HFZ, 
         PB$PerFat_HFZ, 
         show.row.prc = TRUE, 
         show.legend = TRUE)

sjt.xtab(PB$PACER_HFZ, 
         PB$MC_level, 
         show.row.prc = TRUE, 
         show.legend = TRUE)

low <- PB[PB$MCA_Class == 1, ]

high <- PB[PB$MCA_Class == 3, ]

cor.test(low$MCA_Overall, low$PACER_VO2max)

cor.test(high$MCA_Overall, high$PACER_VO2max)

summary(lm(PB$PerFat ~ PB$PACER_VO2max + PB$MCA_Overall))

summary(lm(PB$PerFat ~ PB$MCA_Overall))

summary(lm(PB$PerFat ~ PB$PACER_VO2max))

summary(lm(PB$PACER_VO2max ~ PB$PerFat + PB$MCA_Overall))

boxplot(PB$MCA_Overall, PB$PACER_VO2max)
```

