---
title: "Potential Relevance of a Motor Skill Proficiency Barrier in Youth"
author: "Cade Abrams"
format: 
  html:
    code-copy: true
    code-fold: show
editor: visual
toc: true
self-contained: true
bibliography: PB.bib.bak
---


---
nocite: '@*'
...

# References
:::{#refs}
:::

# Loading Libraries

```{r}
#| output: false

library(tidyverse)
library(here)
library(sjPlot)
library(qwraps2)
library(flextable)
library(officer)
library(apaTables)
```


# Creating Data

## Adding in LOC OC and Stability Composites

```{r}
PB <- read.csv(here("Data", "Clean", "PB.csv"))

extra_data <- read.csv(here("Data", "csv", "De_Meester_Full_Data.csv"))

# Joining percentile data for composites
df_key <- extra_data %>% 
  select(PartJD, MCAStab, MCALoc, MCAOC, MCAOverall)

PB <- PB %>% 
  left_join(df_key,
            by = c("PartID" = "PartJD"))

# Replacing zeros with NA
PB <- PB %>% 
  mutate(MCAStab = replace(MCAStab, MCAStab <= 0, NA),
         MCALoc = replace(MCALoc, MCALoc <= 0, NA),
         MCAOC = replace(MCAOC, MCAOC <= 0, NA),
         MCAOverall = replace(MCAOverall, MCAOverall <= 0, NA))
```

### Making Factors

```{r}
PB <- PB %>% 
  mutate(Grip_level = factor(allo_grip_class,
                             levels = c(1, 2, 3),
                             labels = c("Low", "Moderate", "High")),
         Pacer_level = factor(PACER_HFZ,
                              levels = c(1, 2, 3),
                              labels = c("Health Risk", "Needs Improvement", "Healthy")),
         MC_level = factor(MCA_Class,
                           levels = c(1, 2, 3),
                           labels = c("Low", "Moderate", "High")))

# Making Sex and Ethnicity factors

PB <- PB %>% 
  mutate_at(c("Sex", "Ethnicity"), as.factor)

head(PB)

table(PB$Ethnicity)
```

## Descriptive Statistics

```{r}
#| output: false

# Using qwraps2

descriptives <- subset(PB, select = c(MC_level, Sex, Ethnicity, Age_Test_yrs, StaHt, Weightkg, 
                                      BMI, PACER_VO2max, Grip_Max_Mean_kg, MCAStab, 
                                      MCALoc, MCAOC, MCAOverall))

descriptives

participants <- list("Age" = 
         list("min"       = ~ min(Age_Test_yrs),
              "mean (sd)" = ~ qwraps2 :: mean_sd(Age_Test_yrs),
              "max"       = ~ max (Age_Test_yrs)))

age <- summary_table(descriptives, participants)

age

# Reviewers asked for breakdown by ages (I assume including gender)
descriptives <- descriptives %>% 
  mutate(age_round = floor(Age_Test_yrs)) %>% 
  mutate(age_bins = cut(age_round, 
                        breaks = c(0, 10, 11, 12, 13, 14, 15, 16, 17, 18),
                        labels = c("10", "11", "12", "13", "14", "15", "16", "17", 
                                   "18"),
                        right = TRUE))

sex_age_bin_tib <- descriptives %>% 
  group_by(Sex, age_bins) %>% 
  summarise(N = n()) 

age_bin_tib <- descriptives %>% 
  group_by(age_bins) %>% 
  summarise(N = n())

total_age_bin_tib <- rbind(sex_age_bin_tib, age_bin_tib)

PB %>%
  group_by(Sex, MC_level, Grip_level) %>%
  summarise(Sex_Count=n(), 
            BMI = mean(BMI),
          .groups = "drop")


gender_tib <- descriptives %>%
  group_by(Sex) %>%
  summarise(N = n()) %>%
  mutate(props = round(N/sum(N), 
                       digits = 3)) %>%
 ungroup

ethnic_tib <- descriptives %>%
  group_by(Ethnicity) %>%
  summarise(N = n()) %>%
  mutate(props = round(N/sum(N), 
                       digits = 3)) %>%
 ungroup
```

### APA Table for Descriptive Stats (Packages: qwraps2; flextable; officer)

```{r}
#| eval: false

options(qwraps2_markup = "markdown")
our_summary1 <-
  list("Height (cm)" =
       list("mean (sd)" = ~ qwraps2::mean_sd(StaHt)),
       
       "Weight (kg)" =
       list("mean (sd)" = ~ qwraps2::mean_sd(Weightkg)),
       
       "Vo2 Max" =
       list("mean (sd)" = ~ qwraps2::mean_sd(PACER_VO2max)),
       
       "Grip Max Average (kg)" =
       list("mean (sd)" = ~ qwraps2::mean_sd(Grip_Max_Mean_kg)),
       
       "MCAStab" =
       list("mean (sd)" = ~ qwraps2::mean_sd(MCAStab)),
       
       "MCALoc" =
       list("mean (sd)" = ~ qwraps2::mean_sd(MCALoc)),
       
       "MCAOC" =
       list("mean (sd)" = ~ qwraps2::mean_sd(MCAOC))
       )

whole <- summary_table(descriptives, our_summary1)
whole

level.sum <- summary_table(dplyr::group_by(descriptives, MC_level), our_summary1)
level.sum

level.sum <- as.data.frame(level.sum)

level.sum <- flextable(level.sum %>% rownames_to_column("Delete This Column Header"))

level.sum <- theme_booktabs(level.sum)

level.sum <- align(level.sum, align = "center", part = "body")

level.sum <- set_caption(level.sum, 
                          caption = "Descriptive Statistics of Scores on Level of Motor 
                                     Competence")

level.sum <- footnote(level.sum, 
                      i = 9, 
                      j = 1, 
                      value = as_paragraph("Grip Max Average was calculated by averaging 
                      maximum grip values for the right and left hands."))

level.sum <- autofit(level.sum)

level.sum

MCA_sum <- descriptives %>%
  select(-Sex, -Ethnicity, -age_bins, -age_round) %>% 
  group_by(MC_level) %>%
  summarise(across(everything(), 
                   tibble::lst(mean, sd), 
                   na.rm = TRUE,
                   .names = "{fn}_{col}"))

MCA_sum <- MCA_sum %>% 
  mutate_if(is.numeric, round, 2)

MCA_sum <- t(MCA_sum)

#word_export <- read_docx()
#word_export <- body_add_flextable(word_export, level.sum)
#print(word_export, 'new table.docx')
```

## Looking at Chi-Square for MSF (Packages: sjPlot)

```{r}
PB.new <- subset(PB, select=c(Sex, MC_level, Grip_level, Pacer_level))

sjt.xtab(PB.new$MC_level, 
         PB.new$Grip_level, 
         show.row.prc = TRUE, 
         show.legend = TRUE, 
         file = "apa_GRIP.doc")
```

## Looking at Chi-Square for CRF (Packages: sjPlot)

```{r}
sjt.xtab(PB.new$MC_level, 
         PB.new$Pacer_level, 
         show.row.prc = TRUE, 
         show.legend = TRUE,  
         file = "apa_PACER.doc")
```

# APA Correlation Table for Grip, V02, and MCA Overall (Packages: apaTables)

```{r}
correlations <- subset(PB, select = c(Sex, MCA_Overall, allo_grip_percentile, PACER_VO2max))

apa.cor.table(correlations, table.number = 2)#, filename = "New Correlation Table.doc")
```

